Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-03-03 WSSSPE2_report/WSSSPE2_review.tex
small wording change

\begin{table*}[ht]
\begin{center}
\caption{Barriers to software sustainability, with 0 to 10 `*'s roughly
indicating the fraction of attendees who voted for an item as important}
    \begin{scriptsize}
    \begin{tabular}{ | p{1.65cm} | p{10.0cm} |}
    \hline
  Importance & item \\ \hline \hline
******* & lack of incentives, including promotion and tenure process; promotion
and tenure process in academic is incompatible \\ \hline
*****  & absent / poor documentation \\ \hline
***** & funding difficult \\ \hline
**** & developers are not computer scientists; don't have software engineering
practices (in particular, those needed to scale-up projects to support and be
developed by a large sustainable community) \\ \hline
*** & overreliance on one or two people - bus test \\ \hline
** & rate of change of underlying technologies \\ \hline
** & lack of business models for sustainability \\ \hline
* & lack of training for how to build sustainability into the system \\ \hline
 & maintenance needed for software is not visible, appears to ``just happen'' \\ \hline
 & licensing issues \\ \hline
 & staff turnover - lack of continuity \\ \hline
    \end{tabular}
    \end{scriptsize}
    \label{tb:software_sustainability_barriers}
\end{center}   
\end{table*}

@@

Google doc notes - 
\href{http://tinyurl.com/kqpe87z}
%https://docs.google.com/document/d/1Mivadj16_9tPrw8Nxmhp72AtNC0BEVO-f7M84FXTbSU/edit#heading=h.elaktnt2tep9

@@

Google doc notes - 
\url{http://tinyurl.com/l5t5h45}
%https://docs.google.com/document/d/1G1_U5-hkAvDKtTgT4DvUhIYvyYUY4cBBvQHJIdgADa0/edit#heading=h.v7g0nqpn1fur

@@

{\small
\begin{longtable}{ll}
   Jordan Adams          &  Tulane University
\\ Alice Allen           &  Astrophysics Source Code Library (ASCL)
\\ Gabrielle Allen       &  U Illinois
\\ Pierre-Yves Aquilanti &  TOTAL E\&P R\&T USA
\\ Wolfgang Bangerth
\\ David Bernholdt       &  Oak Ridge National Laboratory
\\ Jakob Blomer
\\ Carl Boettiger        &  UCSC/ropensci
\\ Chris Bogart          &  ISR/CMU
\\ Steven R.~Brandt      &  Louisiana State University
\\ Tom Clune             &  NASA GSFC
\\ John W.~Cobb
\\ Dirk Colbry           &  Michigan State University
\\ Karen Cranston        &  NESCent
\\ Tom Crick             &  Cardiff Metropolitan University, UK
\\ Ethan Davis           &  UCAR Unidata
\\ Robert R Downs        &  CIESIN, Columbia University
\\ Anshu Dubey           &  Lawrence Berkeley National Laboratory
\\ Nicole Gasparini      &  Tulane University, New Orleans
\\ Yolanda Gil           &  Information Sciences Institute, University of Southern California
\\ Kurt Glaesemann       &  Pacific northwest national lab
\\ Sol Greenspan         &  National Science Foundation
\\ Ted Habermann         &  The HDF Group
\\ Marcus D.~Hanwell     &  Kitware
\\ Sarah Harris          &  University of Leeds
\\ David Henty           &  EPCC, The University of Edinburgh
\\ Neil Chue Hong        &  Software Sustainability Institute \& University of Edinburgh
\\ James Howison         &  University of Texas
\\ Maxime Hughes
\\ Eric Hutton           &  University of Colorado
\\ Ray Idaszak           &  RENCI/UNC
\\ Samin Ishtiaq         &  Microsoft Research Cambridge, UK
\\ Matt Jones            &  University of California Santa Barbara
\\ Nick Jones            &  New Zealand eScience Infrastructure, University of Auckland
\\ Daniel S.~Katz        &  U Chicago \& Argonne
\\ Ian Kelley
\\ Hilmar Lapp           &  National Evolutionary Synthesis Center (NESCent) and Duke University
\\ Chris Lenhardt
\\ Richard Littauer      &  MIT/University of Saarland
\\ Frank L\"{o}ffler     &  Louisiana State University
\\ Andre Luckow          &  Rutgers
\\ Berkin Malkoc         &  Istanbul Technical University
\\ Kyle Marcus           &  University at Buffalo
\\ Bryan Marker          &  The University of Texas at Austin
\\ Suresh Marru          &  Indiana University
\\ Robert H.~McDonald    &  Indiana University - Data to Insight Center/Libraries
\\ Rupert Nash
\\ Andy Nutter-Upham     &  Whitehead Institute
\\ Abani Patra           &  University at Buffalo
\\ Aleksandra Pawlik     &  Software Sustainability Institute
\\ Cody J.~Permann       &  Idaho National Laboratory
\\ John W.~Peterson      &  Idaho National Laboratory
\\ Benjamin Pharr        &  University of Mississippi
\\ Stephen Piccolo       &  Brigham Young University, Utah
\\ Marlon Pierce         &  Indiana University
\\ Ray Plante            &  NCSA/University of Illinois Urbana-Champaign
\\ Sushil Prasad         &  Georgia State University, Atlanta
\\ Karthik Ram           &  University of California, Berkeley. Berkeley Institute for Data Science and rOpenSci
\\ Mike Rilee            &  NASA/GSFC, Rilee Systems Technologies
\\ Erin Robinson         &  Foundation for Earth Science
\\ Mark Schildhauer      &  NCEAS, Univ. California, Santa Barbara
\\ Jory Schossau         &  Michigan State University
\\ Frank Seinstra        &  Netherlands eScience Center
\\ James Shepherd        &  Rice University
\\ Justin Shi
\\ Ardita Shkurti        &  University of Nottingham
\\ Alan Simpson          &  EPCC, The University of Edinburgh
\\ Carol Song            &  Purdue University
\\ James Spencer         &  Imperial College London
\\ Tracy Teal            &  Data Carpentry
\\ Kaitlin Thaney        &  Mozilla Science Lab
\\ Matt Turk             &  NCSA/UIUC
\\ Colin C.~Venters      &  University of Huddersfield
\\ Nathan Weeks
\\ Ethan White           &  University of Florida/Utah State University
\\ Nancy Wilkins-Diehr   &  SDSC
\\ Greg Wilson           &  Software Carpentry
\end{longtable}
}

>>>>

\begin{table*}[ht]
\begin{center}
\caption{Barriers to software sustainability, with 0 to 10 `*'s roughly
indicating the fraction of attendees who voted for an item as important}
    \begin{scriptsize}
    \begin{tabular}{ | p{1.65cm} | p{10.0cm} |}
    \hline
  Importance & item \\ \hline \hline
******* & lack of incentives, including promotion and tenure process; promotion
and tenure process in academic is incompatible with sustainability \\ \hline
*****  & absent or poor documentation \\ \hline
***** & funding to ensure sustainability is difficult to obtain \\ \hline
**** & developers are not computer scientists; don't have software engineering
practices (in particular, those needed to scale-up projects to support and be
developed by a large sustainable community) \\ \hline
*** & overreliance on one or two people - bus test \\ \hline
** & rate of change of underlying technologies \\ \hline
** & lack of business models for sustainability \\ \hline
* & lack of training for how to build sustainability into the system \\ \hline
 & maintenance needed for software is not visible, appears to ``just happen'' \\ \hline
 & licensing issues \\ \hline
 & staff turnover - lack of continuity \\ \hline
    \end{tabular}
    \end{scriptsize}
    \label{tb:software_sustainability_barriers}
\end{center}   
\end{table*}

@@

google doc notes - \url{http://tinyurl.com/kqpe87z}
%https://docs.google.com/document/d/1Mivadj16_9tPrw8Nxmhp72AtNC0BEVO-f7M84FXTbSU/edit#heading=h.elaktnt2tep9

@@

google notes doc - 
\url{http://tinyurl.com/l5t5h45}
%https://docs.google.com/document/d/1G1_U5-hkAvDKtTgT4DvUhIYvyYUY4cBBvQHJIdgADa0/edit#heading=h.v7g0nqpn1fur

@@

{\small
\begin{longtable}{ll}
   Jordan Adams          &  Tulane University
\\ Alice Allen           &  Astrophysics Source Code Library (ASCL)
\\ Gabrielle Allen       &  U Illinois
\\ Pierre-Yves Aquilanti &  TOTAL E\&P R\&T USA
\\ Wolfgang Bangerth
\\ David Bernholdt       &  Oak Ridge National Laboratory
\\ Jakob Blomer
\\ Carl Boettiger        &  UCSC/ropensci
\\ Chris Bogart          &  ISR/CMU
\\ Steven R.~Brandt      &  Louisiana State University
\\ Tom Clune             &  NASA GSFC
\\ John W.~Cobb
\\ Dirk Colbry           &  Michigan State University
\\ Karen Cranston        &  NESCent
\\ Tom Crick             &  Cardiff Metropolitan University, UK
\\ Ethan Davis           &  UCAR Unidata
\\ Robert R Downs        &  CIESIN, Columbia University
\\ Anshu Dubey           &  Lawrence Berkeley National Laboratory
\\ Nicole Gasparini      &  Tulane University, New Orleans
\\ Yolanda Gil           &  Information Sciences Institute, University of Southern California
\\ Kurt Glaesemann       &  Pacific northwest national lab
\\ Sol Greenspan         &  National Science Foundation
\\ Ted Habermann         &  The HDF Group
\\ Marcus D.~Hanwell     &  Kitware
\\ Sarah Harris          &  University of Leeds
\\ David Henty           &  EPCC, The University of Edinburgh
\\ Neil Chue Hong        &  Software Sustainability Institute \& University of Edinburgh
\\ James Howison         &  University of Texas
\\ Maxime Hughes
\\ Eric Hutton           &  University of Colorado
\\ Ray Idaszak           &  RENCI/UNC
\\ Samin Ishtiaq         &  Microsoft Research Cambridge, UK
\\ Matt Jones            &  University of California Santa Barbara
\\ Nick Jones            &  New Zealand eScience Infrastructure, University of Auckland
\\ Daniel S.~Katz        &  U Chicago \& Argonne
\\ Ian Kelley
\\ Hilmar Lapp           &  National Evolutionary Synthesis Center (NESCent) and Duke University
\\ Chris Lenhardt
\\ Richard Littauer      &  MIT/University of Saarland
\\ Frank L\"{o}ffler     &  Louisiana State University
\\ Andre Luckow          &  Rutgers
\\ Berkin Malkoc         &  Istanbul Technical University
\\ Kyle Marcus           &  University of Buffalo
\\ Bryan Marker          &  The University of Texas at Austin
\\ Suresh Marru          &  Indiana University
\\ Robert H.~McDonald    &  Indiana University - Data to Insight Center/Libraries
\\ Rupert Nash
\\ Andy Nutter-Upham     &  Whitehead Institute
\\ Abani Patra           &  Univ @ Buffalo
\\ Aleksandra Pawlik     &  Software Sustainability Institute
\\ Cody J.~Permann       &  Idaho National Laboratory
\\ John W.~Peterson      &  Idaho National Laboratory
\\ Benjamin Pharr        &  University of Mississippi
\\ Stephen Piccolo       &  Brigham Young University, Utah
\\ Marlon Pierce         &  Indiana University
\\ Ray Plante            &  NCSA/University of Illinois Urbana-Champaign
\\ Sushil Prasad         &  Georgia State University, Atlanta
\\ Karthik Ram           &  University of California, Berkeley. Berkeley Institute for Data Science and rOpenSci
\\ Mike Rilee            &  NASA/GSFC, Rilee Systems Technologies
\\ Erin Robinson         &  Foundation for Earth Science
\\ Mark Schildhauer      &  NCEAS, Univ. California, Santa Barbara
\\ Jory Schossau         &  Michigan State University
\\ Frank Seinstra        &  Netherlands eScience Center
\\ James Shepherd        &  Rice University
\\ Justin Shi
\\ Ardita Shkurti        &  University of Nottingham
\\ Alan Simpson          &  EPCC, The University of Edinburgh
\\ Carol Song            &  Purdue University
\\ James Spencer         &  Imperial College London
\\ Tracy Teal            &  Data Carpentry
\\ Kaitlin Thaney        &  Mozilla Science Lab
\\ Matt Turk             &  NCSA/UIUC
\\ Colin C.~Venters      &  University of Huddersfield
\\ Nathan Weeks
\\ Ethan White           &  University of Florida/Utah State University
\\ Nancy Wilkins-Diehr   &  SDSC
\\ Greg Wilson           &  Software Carpentry
\end{longtable}
}
